Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
backup commit
updated paper.tex

\begin{figure}[hbct]
    {\footnotesize\input{pictures/freq_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

@@

\begin{figure}
    {\footnotesize\input{pictures/freqrange}}
    \caption{
        The covered frequency range for an unoptimized
        genotype $G_0$ as well as genotypes $G\ix{high}$ and $G\ix{low}$
        that are optimized for $C\ix{high}$ respectively $C\ix{low}$. Each
        of the three genotypes was tested against constant challenges
        $C_\omega$ that yielded simple sinusoidal waves with frequency
        $\omega$ for every seed value. The topology of all genotypes was
        a mere Erdös-Renyi topology.
        The parameters for the unoptimized genotype $G_0$ were taken to be
        default values from \cite{FORCE} (which also uses Erdös-Renyi
        topologies), while we chose genotypes $G\ix{high}$ and $G\ix{low}$
        that did particularly well when explicitly optimizing for high and
        low frequencies (see FIG. \ref{fig:freq_optimization} for more
        details).
    }
    \label{fig:freqrange}
\end{figure}

@@

\begin{figure}[hbct]
    {\footnotesize\input{pictures/top_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

>>>>

\begin{figure}
    {\footnotesize\input{pictures/freq_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

@@

\begin{figure}
    {\footnotesize\input{pictures/freqrange}}
    \caption{
        The covered frequency range for an unoptimized
        genotype $G_0$ as well as genotypes $G\ix{high}$ and $G\ix{low}$
        that are optimized for $C\ix{high}$ respectively $C\ix{low}$. Each
        of the three genotypes was tested against constant challenges
        $C_\nu$ that yielded simple sinusoidal waves with frequency
        $\nu$ for every seed value. The topology of all genotypes was
        a mere Erdös-Renyi topology.
        The parameters for the unoptimized genotype $G_0$ were taken to be
        default values from \cite{FORCE} (which also uses Erdös-Renyi
        topologies), while we chose genotypes $G\ix{high}$ and $G\ix{low}$
        that did particularly well when explicitly optimizing for high and
        low frequencies (see FIG. \ref{fig:freq_optimization} for more
        details).
    }
    \label{fig:freqrange}
\end{figure}

@@

\begin{figure}[]
    {\footnotesize\input{pictures/top_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}
